Assignment 3

### 2019-07-31 ex3/report/report.tex

In particular,  \autoref{fig:pdp} shows the Partial Dependency Plots (PDP) for the source and destination port features. If $\boldsymbol X \in \mathbb R ^n$ denotes a random vector drawn from feature space and $f(X) \in [0,1]$ denotes the neural network's prediction, the PDP for feature $i$ can be defined as 
\begin{equation} \label{eq:pdp}
\text{PDP}_i(y) = \mathbb E_{\boldsymbol X}\left(f(X_1,\ldots,X_{i-1},y,X_{i+1},\ldots X_n)\right)
\end{equation}

As apparent from \autoref{fig:pdp}, for a certain value of the $i$th feature, the whole dataset is used for averaging the neural network's outcome.

We also experiment with a modified definition of the PDP (with C being the distribution of attack classes): 
\begin{equation} \label{eq:pdp_conditional}
\text{PDP}_{c,i}(y) = \mathbb E_{\boldsymbol X | C = c} \left(f \left( X_1,\ldots,X_{i-1},y,X_{i+1},\ldots X_n \right) \right)
\end{equation}

>>>>

In particular,  in literature the use of Partial Dependency Plots (PDP) is proposed. If $\boldsymbol X \in \mathbb R ^n$ denotes a random vector drawn from feature space and $f(X) \in [0,1]$ denotes the neural network's prediction, the PDP for feature $i$ can be defined as
\begin{equation} \label{eq:pdp}
\text{PDP}_i(y) = \mathbb E_{\boldsymbol X}\left(f(X_1,\ldots,X_{i-1},y,X_{i+1},\ldots X_n)\right)
\end{equation}

To capture similarity between attack families, we in this research experiment with a modified definition of the PDP  (with C being the attack classes):
\begin{equation} \label{eq:pdp_conditional}
\text{PDP}_{c,i}(y) = \mathbb E_{\boldsymbol X | C = c} \left(f \left( X_1,\ldots,X_{i-1},y,X_{i+1},\ldots X_n \right) \right)
\end{equation}
